---
title: "Mid-summury"
author: "JuwonOh"
date: '`r Sys.Date()`'
fontsize: 12pt
output: 
  html_document: default

---

```{r, results='hide', warning=FALSE, message=FALSE}

library(dplyr)
library(knitr)
library(readr)
library(stringr)
library(tm)
library(Cairo)
library(quanteda)
library(tidyverse)
library(tidytext)
library(lattice)
library(stm)        # Package for sturctural topic modeling
library(stmCorrViz) # Package for hierarchical correlation view of STMs
require(splines)
library("zoo")

# user specific working directory setup and loading news data

setwd('~/Dropbox/Press release')
source('code/help.R', encoding="utf-8")
```

### Exploring the effects of the covariates: Party

```{r fig.height = 10, fig.width = 20, echo=TRUE, results="hide"}
load('data/senate-merging-election.Rdata')
## Independent seantors were excluded to leave only the topic distribution by party.
senate.party <- subset(senate_df, party == 'D' | party =='R')

### Preprocessing

out <- preproc(senate.party)
vocab <- out$vocab
meta <- out$meta

meta$trump.datrs <- as.numeric(meta$trump.dates)

seed = 19999
congressPrevFitAll <- stm(out$documents, out$vocab, K=30,
                          prevalence=~ party+ s(trump.dates) + region + pre16 ,
                          max.em.its=75, data=out$meta, init.type="Spectral", seed=seed)

prepAll30 <- estimateEffect(1:30 ~ party + s(trump.dates, df = 30) + region + pre16, congressPrevFitAll,
                            meta = out$meta, uncertainty = "Global", prior = 0.01)
```

```{r echo=FALSE}
Result <- plot(
  prepAll30,
  "party",
  method = "difference",
  cov.value1 = "R",
  cov.value2 = "D",
  verbose.labels = F,
  ylab = "Expected Difference in Topic Probability by Party (with 95% CI)",
  xlab = "More Likely Republican                          Not Significant                       More Likely Democrat",
  main = "Effect of Party on Topic Prevelance for Press Release",
  xlim = c(-0.1, 0.1)
)

topicNames <- labelTopics(congressPrevFitAll, n = 5)
topic <- data.frame(
  TopicNumber = 1:30,
  TopicProportions = colMeans(congressPrevFitAll$theta))
```

```{r echo=FALSE fig.width=100, fig.height=80}
# order based on Expected Topic Proportion
rank = order(unlist(Result$means))
topicRnk <- topic[rank, ]

plot(
  prepAll30,
  "party",
  method = "difference",
  cov.value1 = "R",
  cov.value2 = "D",
  verbose.labels = F,
  topics = topicRnk$TopicNumber,
  ylab = "Expected Difference in Topic Probability by Party (with 95% CI)",
  xlab = "More Likely Republican                          Not Significant                       More Likely Democrat",
  main = "Effect of Party on Topic Prevelance for Press Release",
  xlim = c(-0.2, 0.2)
)
devtools::install_github("mikaelpoul/tidystm", dependencies = TRUE)

main = paste0(model.stm.labels$prob[i,1:3])
```

### Summary of Statistics

You can also embed plots, for example:

```{r}

out <- preproc(senate_df)
docs <- out$documents
vocab <- out$vocab
meta <- out$meta

meta$trump.datrs <- as.numeric(meta$trump.dates)

### Preprocessing

load('data/stm data/congressPrevFit.Rdata')
prep <- estimateEffect(1:30 ~ party + s(trump.dates), congressPrevFit,
                        meta = out$meta, uncertainty = "Global", prior = 0.01)
summary(prep, topics=14) 

```

```{r}

load('data/stm data/congressPrevFitS.Rdata')
prepS <- estimateEffect(1:30 ~ party + trump.binary + state, congressPrevFitS,
                         meta = out$meta, uncertainty = "Global", prior = 0.01)

summary(prepS, topics=14)

```

```{r}

load('data/stm data/congressPrevFitR.Rdata')
prepR <- estimateEffect(1:30 ~ party + s(trump.dates) + region, congressPrevFitR,
                         meta = out$meta, uncertainty = "Global", prior = 0.01)
summary(prepR, topics=14)

```

```{r}

load('data/stm data/congressPrevFitAlldf30.Rdata')
prepAll30 <- estimateEffect(1:30 ~ party + s(trump.dates, df = 30) + region + pre16, congressPrevFitAll,
                          meta = out$meta, uncertainty = "Global", prior = 0.01)
summary(prepR, topics=14)
```

```{r}
load('data/stm data/congressPrevFitAlldf20.Rdata')

prepAll20 <- estimateEffect(1:30 ~ party + s(trump.dates, df = 20) + region + pre16, congressPrevFitAll,
                            meta = out$meta, uncertainty = "Global", prior = 0.01)
summary(prepAll20, topics=14)
```

### Effect of Time

```{r}
## Create a daily Date object - helps my work on dates
inds <- seq(as.Date("2015-01-01"), as.Date("2018-08-30"), by = "day")
xx <- sort(unique(out$meta$trump.dates))
xx.dates <- as.Date(as.numeric(xx), origin ='2016-11-08')

## Create a time series object and define b-spline
set.seed(25)
myts <- ts(xx,     # random data
           start = c(2015, as.numeric(format(inds[1], "%j"))),
           frequency = 365)
tbs <- bs(xx, degree=30)
bsts14 <- ts(tbs[,14],     # random data
             start = c(2015, as.numeric(format(inds[1], "%j"))),
             frequency = 365)
bsts18 <- ts(tbs[,18],     # random data
             start = c(2015, as.numeric(format(inds[1], "%j"))),
             frequency = 365)
bsts26 <- ts(tbs[,26],     # random data
            start = c(2015, as.numeric(format(inds[1], "%j"))),
            frequency = 365)

plot(bsts26, col="red")
lines(bsts18, col="green")
lines(bsts14, col="blue")

```

```{r fig.width=60, fig.height=80}
## which date is the maximum of bsts 7 degree?
time(bsts14)[which.max(bsts14)]
time(bsts18)[which.max(bsts18)]
time(bsts26)[which.max(bsts26)]

## Changes in topic proportion over time

major.topics <- c(10, 14, 30, 13)
topics = 30
monthseq <- seq(from=as.Date("2015-01-01"), to=as.Date("2018-08-29"), by="month")
monthnames <- months(monthseq)
model.stm.labels <- labelTopics(congressPrevFitAll, major.topics)
labelsname <- c('topic 10 : trade, steel, workers', 'topic 14 : american, jobs, agreement',
                'topic 30 : tariffs, trump, administration', 'topic 13 : program, infrastructure, funding')
labelsname[1]
par(mfrow=c(4,1), cex.lab=3, cex.axis=3, cex.main=5)
for (i in 1:4){
  plot.estimateEffect(prepAll30, "trump.dates", method = "continuous", topics = major.topics[i], main = labelsname[i],
       printlegend = F, xaxt='n', ylim=c(-.10,.30))
  axis(1,at=c(-676,-309, 56, 420),labels=c(2015,2016,2017,2018),las=2)
  abline(v=c(-676,-309, 56, 420),lty=2,lwd=1,col="grey45") 
  # spline axis
  axis(1,at=c(-252,-134, 120),labels=c('s14','s18','s26'),las=2)
  abline(v=c(-252,-134, 120),col="blue")
  # president election
  axis(1,at=c(1),labels=c('President Election'),las=2)
  abline(v=c(1),col="green")
}

```


### Using CausalImpact

### Using Stargazer or Xtable

## Model A. Select losers and winners only (senators who lost seats and who won seats in the same state)

### Summary of Statistics

```{r}

load('data/groupAtext.Rdata')
start.date = "2016-01-01"
outA <- preproc(groupA)
docsA <- outA$documents
vocabA <- outA$vocab
metaA <- outA$meta
metaA$trump.datrs <- as.numeric(metaA$trump.dates)

```

```{r echo=FALSE}
load('data/stm data/congressPrevFitAAll.Rdata')
congressPrevFitAAll <- stm(outA$documents, outA$vocab, K=30,
                           prevalence=~ party + state + s(trump.dates) + region + pre16 ,
                           max.em.its=75, data=outA$meta, init.type="Spectral", seed=seed)
```

```{r}
prepAAll <- estimateEffect(1:30 ~ party + state + s(trump.dates) + region + pre16, congressPrevFitAAll,
                         meta = outA$meta, uncertainty = "Global", prior = 0.01)
summary(prepAAll, topics=3)
```

## Model C. Select senators who continue to serve before and after the election (including winners of the 2016 election)

### Summary of Statistics


```{r echo=FALSE}

load('data/groupCtext.Rdata')
start.date = "2016-01-01"
outC <- preproc(groupC)
docsC <- outC$documents
vocabC <- outC$vocab
metaC <- outC$meta
metaC$trump.datrs <- as.numeric(metaC$trump.dates)

```

```{r echo=FALSE}
congressPrevFitCAll <- stm(outC$documents, outC$vocab, K=30,
                           prevalence=~ party + state + s(trump.dates, df = 20) + region + pre16 ,
                           max.em.its=75, data=outC$meta, init.type="Spectral", seed=seed)
```

```{r}
prepCAll <- estimateEffect(1:30 ~ party + state + s(trump.dates, df =20) + region + pre16, congressPrevFitCAll,
                         meta = outC$meta, uncertainty = "Global", prior = 0.01)
summary(prepCAll, topics=17) 

```

## Model D. Select senators who did not go through the 2016 election (only off-election senatros)

### Summary of Statistics

```{r echo=FALSE}

load('data/groupDtext.Rdata')

## Preprocessing

start.date = "2016-01-01"
outD <- preproc(groupD)
docsD <- outD$documents
vocabD <- outD$vocab
metaD <- outD$meta
metaD$trump.datrs <- as.numeric(metaD$trump.dates)
```

```{r}
load('data/stm data/congressPrevFitDAll.Rdata')
prepDAll <- estimateEffect(1:30 ~ party + s(trump.dates) + region + pre16, congressPrevFitDAll,
                        meta = outD$meta, uncertainty = "Global", prior = 0.01)
summary(prepDAll, topics=5) 
```

