---
title: "Public newss about korea"
author: "Juwon Oh"
date: "2019년 6월 02일"
output: html_document
---

## Introduction


## Data


## Loading package and data

```{r, results='hide', warning=FALSE, message=FALSE}
library(knitr)
library(readr)
library(stringr)
library(tm)
library(Cairo)
library(quanteda)
library(tidyverse)
library(tidytext)
library(lattice)
library(stm)        # Package for sturctural topic modeling
library(stmCorrViz) # Package for hierarchical correlation view of STMs
# user specific working directory setup and loading news data

if(Sys.getenv("LOGNAME") == "park"){
    setwd("~/Dropbox/press release")
    source("~/Github/Sooahn/GlobalDataCenter/Analysis/preprocess_functions.R")

}else{
    setwd('~/Dropbox/Press release')
    source("~/github/GlobalDataCenter/Analysis/preprocess_functions.R")
}
load('data/trade house.Rdata')
source('code/help.R')
```

## Preprocessing
```{r}
h_out <- preproc(house)

h_docs <- h_out$documents
h_vocab <- h_out$vocab
h_meta <- h_out$meta
```

### divide data by two regimes
```{r}
house$numeric.date <- as.Date(house$date) - as.Date('2015-01-01')
house1 <- subset(house, numeric.date < 683)
house2 <- subset(house, numeric.date >= 683)
## house[which(house$numeric.date == 683), 8:10]
##      year month day
## 1321 2016    11  14

## pre
h_out1 <- preproc(house1)
h_docs1 <- h_out1$documents
h_vocab1 <- h_out1$vocab
h_meta1 <- h_out1$meta

## post
h_out2 <- preproc(house2)
h_docs2 <- h_out2$documents
h_vocab2 <- h_out2$vocab
h_meta2 <- h_out2$meta
```



## Using stm

## Understand and Explain

```{r, results='hide', warning=FALSE}
seed = 3729 ## sample(1:10000, 1)
housePrevFit <- stm(h_out$documents, h_out$vocab, K=30, prevalence=~party+state+s(date),  max.em.its=75, data=h_out$meta,
                        init.type="Spectral", seed=seed)

## pre
housePrevFit1 <- stm(h_out1$documents, h_out1$vocab, K=30, prevalence=~party+state+s(date),  max.em.its=75, data=h_out1$meta,
                        init.type="Spectral", seed=seed)

## post
housePrevFit2 <- stm(h_out2$documents, h_out2$vocab, K=30, prevalence=~party+state+s(date),  max.em.its=75, data=h_out2$meta,
                        init.type="Spectral", seed=seed)

## save(housePrevFit, file = "data/house_stm.Rdata")
```

### Proportion of topics

- 전체 문서에서 각 토픽들이 차지하는 비중을 살펴보자.

```{r, fig.width=10, fig.height=8}
par(bty="n",col="grey40",lwd=5)
plot(housePrevFit, type="summary", xlim=c(0,.4))

par(bty="n",col="grey40",lwd=5)
plot(housePrevFit1, type="summary", xlim=c(0,.4))

par(bty="n",col="grey40",lwd=5)
plot(housePrevFit2, type="summary", xlim=c(0,.4))
```

### label of topics
```{r}
label <- labelTopics(housePrevFit, n = 10)
## highest probability words
Prob <- label[1]$prob
## FREX: exclusivity in a way that balances word frequency. FREX is the weighted harmonic mean of the word’s rank in terms of exclusivity and frequency.
Frex <- label[2]$frex
## Lift weights words by dividing by their frequency in other topics, therefore giving higher weight to words that appear less frequently in other topics.
Lift <- label[3]$lift
## score divides the log frequency of the word in the topic by the log frequency of the word in other topics. 
Score <- label[4]$score
## label[5]$topicnums
```


### print the documents highly associated with each topic
```{r}
## the first 200 characters of original text.
shortdoc <- house$title[-252]
findText(housePrevFit, texts = shortdoc, n = 20, topics = 25)
findText(housePrevFit, texts = shortdoc, n = 20, topics = 11)
findText(housePrevFit, texts = shortdoc, n = 20, topics = 20)
findText(housePrevFit, texts = shortdoc, n = 20, topics = 17)
findText(housePrevFit, texts = shortdoc, n = 20, topics = 24)
findText(housePrevFit, texts = shortdoc, n = 20, topics = 26)

## what we want to find
## 1. topic change (does trade issue change after the election?)
## 2. who issues press release in relevant topics? (by state, party, district)
## 3. how the frequency, number of legislators, change before and after the election?

## pre
shortdoc1 <- house1$title[-252]
findText(housePrevFit1, texts = shortdoc1, n = 20, topics = 26)


## post
shortdoc2 <- data$title[-252]
```


### Keywords in topics

- 각 토픽에서 주요한 단어들을 볼 수 있다.

```{r, fig.width=10, fig.height=8}
plot(housePrevFit, type="labels", topics=c(24,10, 16, 23, 15, 19, 27, 27))
```


```{r}
print(sageLabels(housePrevFit))
```

### Topics labeling 

```{r, fig.width=8, fig.height=8}
mod.out.corr <- topicCorr(housePrevFit)
plot(mod.out.corr,  
     topics = c(1:30))
```

### EstimateEffect

 - STM은 estimateEffect함수를 통해서 topical prevalence와 메타데이터들 사이의 관계를 관측한다. 사용자는 메타데이터의 변수를 지정하여 topic들을 estimate 한다. 이를 통해 특정 주제에 대한 문서의 비율을 볼 수 있으며, 주제에 따라 변수들이 어떤 상관관계를 가졌는지, 그 정도가 시간의 흐름에 따라 어떻게 변화하는지 볼 수 있다.
 - estimateEffect 함수의 결과는 회귀 분석의 결과와 비슷하게 정리된다.
 - 첫번째 예시는 토픽과 변수(씽크탱크)의 상관관계를 살펴본 것이다.
 
```{r, results='hide', warning=FALSE}
h_out$meta$party <- as.character(h_out$meta$party)
h_out$meta$state <- as.character(h_out$meta$state)
prep_h <- estimateEffect(1:30 ~ party+state+s(date), housePrevFit, h_meta=h_out$meta, 
                       uncertainty="Global")
```



```{r, fig.width=10, fig.height=8}
plot(prep_h, covariate="party", topics= c(10,1, 11, 12, 13, 6, 8, 9), model=housePrevFit, 
     method="difference", cov.value1="R", cov.value2='D',
     xlab="Republicans vs. Democrats", main="Effect of Republicans vs. Democrats",
     xlim=c(-.30,.30))
```


```{r, fig.width=20, fig.height=60}
## PLOT 함수에서 GGPLOT으로 바꾸기. 제대로 안나옴. 1) 토픽을 늘리건, 2) hLDA를 사용하건, 좀더 토픽이 심층적으로 나오게 살펴보기.
par(mfrow=c(15,1), pin=c(100,100))
topics = 15
monthseq <- seq(from=as.Date("2015-01-01"), to=as.Date("2019-06-15"), by="month")
monthnames <- months(monthseq)

model.stm.labels <- labelTopics(housePrevFit, 1:topics)
labelsname <- c('topic 1', 'topic 2', 'topic 3', 'topic 4', 'topic 5', 'topic 6', 'topic 7', 'topic 8', 'topic 9', 'topic 10','topic 11', 'topic 12', 'topic 13', 'topic 14', 'topic 15')

for (i in c(1:15))
{
  plot(prep_h, "date", method="continuous", topics = i, main = labelsname[i], printlegend = F,
       xaxt="n", xlab="Time", ylim=c(-.10,.30))
  axis(1, at=as.numeric(monthseq)-min(as.numeric(monthseq)), labels=monthnames)
}


```
